# Markdown example with knitr and googleVis
===========================================
This is a little Markdown example file. It uses googleVis package with knitr and markdown to produce interactive plots from **Google Visualization API**.

In this case change the behaviour of plot.gvis, so that it presents only 
the code for the chart rather than making a full web page.

```{r setOptions, message=FALSE}
library(googleVis)
op <- options(gvis.plot.tag='chart')
```
The following plot statements will automatically return  the HTML
required for the 'knitted' output. 
 

## Pie chart
example pie charts

Let's take a look at the data:
```{r}
head(CityPopularity)
```
Now plot the pie chart
```{r gvisPieChart, results='asis'}

Pie <- gvisPieChart(CityPopularity,
                    options=list(width=400, height=200))
plot(Pie)
```

## Place two charts next to each other
Example of a gvisGeoChart with gvisTable
Let's have a look at the data first
```{r}
head(Exports)
```

```{r gvisMergeExample, results='asis', echo=FALSE}
Geo <- gvisGeoChart(Exports, locationvar='Country', colorvar='Profit', 
                    options=list(height=300, width=350)) 
Tbl <- gvisTable(Exports, options=list(height=300, width=200))
plot(gvisMerge(Geo, Tbl, horizontal=TRUE))
``````

 
 
## Scatter Plot
Scatter plot example with googleVis
```{r}
head(women)
```
This time we will be able to edit the plot since we set `gvis.editor` argument.
```{r ScatterPlotExample, results='asis', tidy=TRUE}

Scatter1 <- gvisScatterChart(women,
                             options=list(
                               gvis.editor="edit",vAxis="{title:'weight (lbs)'}",
                    hAxis="{title:'height (in)'}"))
plot(Scatter1)
```

## Intensity Map

```{r}
df=data.frame(country=c("US", "GB", "BR"), val1=c(1,3,4), val2=c(23,12,32))
head(df)
```

```{r IntensityExample, results='asis', tidy=TRUE}

Intensity1 <- gvisIntensityMap(df, locationvar="country", numvar=c("val1", "val2"))
plot(Intensity1)
```


## Combo chart
```{r ComboExample, results='asis', tidy=FALSE}
## Add the mean
CityPopularity$Mean=mean(CityPopularity$Popularity)
CC <- gvisComboChart(CityPopularity, xvar='City',
          yvar=c('Mean', 'Popularity'),
          options=list(seriesType='bars',
                       width=450, height=300,
                       title='City Popularity',
                       series='{0: {type:\"line\"}}'))
plot(CC)
```

```{r resetOptions}
## Set options back to original options
options(op)
```