# Markdown example with knitr and rCharts
===========================================
This is an example file showing how to use rCharts with knitr/markdown. **rCharts** an R package to create, customize and publish interactive javascript visualizations from R.

Let's first install it, it lives on github, not on CRAN yet.
```{r,eval=FALSE}
require(devtools)
install_github('rCharts', 'ramnathv', ref = 'dev')
```


## Scatter plot using polychart

```{r, results='asis',out.width=400}
require(rCharts)
add_lib_assets("Polycharts")
names(iris) = gsub("\\.", "", names(iris))
rPlot(SepalLength ~ SepalWidth | Species, data = iris, color = 'Species', type = 'point')
```

## Multi barchart using NVD3
```{r nvd3mbar, results='asis',comment=NA}
add_lib_assets("NVD3")
hair_eye_male <- subset(as.data.frame(HairEyeColor), Sex == "Male")
n1 <- nPlot(Freq ~ Hair, group = "Eye", data = hair_eye_male, type = "multiBarChart")
n1$print("nvd3mbar")
```


## Scatter Plot from NVD3
Scatter plot example with rCharts using NVD3 JS library
```{r nvd3Scatter, results='asis',comment=NA}
data(iris)
sepal <- iris[,c(1:2,5)]
add_lib_assets("NVD3")
n2 <- nPlot(Sepal.Length ~ Sepal.Width, data =sepal, type = "scatterChart",group="Species")
n2$print("vd3Scatter")

```

